### 2023-06-22 appendix.tex
up

First, let us recall the home-state problem: 
whether a state $s$ is such that, for all state $s_0$ there exists a path from $s_0$ to $s$.

Home-state is undecidable for Minsky machine with $3+$ counters.

Because $2$-counter Minsky machine termination is undecidable.

$2$-counter Minsky machine $M$, one can construct a $3$-counter Minsky machine $M'$ which 
third counter starts at least at $1$, and simulates $M$ until it reaches a control state indicative of termination, then lower the first two counters until they reach $0$, then finally lower the third counter until it reaches $0$.

Then the Minsky machine $M$ terminates for all inputs iff the Minsky machine $M'$ can reach $(0,0,0)$ from any input with at least $1$ on its third counter.

@@

Thus home-state/resilience is undecidable for Minsky machines.

>>>>

First, let us recall the home-state problem

\problemx{Home-state}
{A transition system $\mathscr{S}=(S,\rightarrow)$ and a state $s \in S$.}
{$S \longrightarrow^{*} \{s\}$ ?\newline}

% whether a state $s$ is such that, for all state $s_0$ there exists a path from $s_0$ to $s$.

Home-state is undecidable for Minsky machine with $3+$ counters.
This stems from the fact $2$-counter Minsky machine termination is undecidable~\cite{Min61, Min67}.
From a $2$-counter Minsky machine $M$, one can construct a $3$-counter Minsky machine $M'$ 
such that the Minsky machine $M$ terminates for all inputs iff the Minsky machine $M'$ can reach $(0,0,0)$ from any input with at least $1$ on its third counter. We build $M'$ to simulate $M$ until it reaches a control state indicative of termination, then lower the first two counters until they reach $0$, then finally lower the third counter until it reaches $0$.

@@

Thus {\sc Home-state} is undecidable for Minsky machines. Hence {\sc Resilience} is undecidable.
